---
title: "CamCan Preliminary Analysis"
author: "Kyle Kurkela"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    df_print: paged
    code_folding: hide
---

```{r echo = FALSE, message = FALSE}
suppressPackageStartupMessages(library(tidyverse))
```

```{r}
fd_mean_thresh <- 0.3
num_runs_thresh <- 1
age_thresh <- 50
```

```{r}
motion <- read_rds('motion.rds')

motion %>%
  mutate(CCID = str_remove(CCID, 'sub-')) -> motion

head(motion)
```

```{r paged.print=TRUE}
df <- read_rds('data.rds')

motion %>% 
  filter(task == 'movie') %>%
  group_by(CCID) %>%
  summarise(BadMotion = sum(fd_mean > fd_mean_thresh), .groups = 'drop') %>%
  mutate(BadMotion = BadMotion > 1) %>%
  add_column(task = 'movie') -> movie

motion %>%
  filter(task != 'movie') %>%
  mutate(BadMotion = fd_mean > fd_mean_thresh) %>%
  select(CCID, task, BadMotion) %>%
  bind_rows(., movie) %>%
  group_by(CCID) %>%
  summarise(ExcludeMotion = sum(BadMotion) > num_runs_thresh, .groups = 'drop') -> motion.summary

df %>% 
  left_join(., motion.summary, by = 'CCID') %>%
  mutate(ExcludeMotion = if_else(is.na(ExcludeMotion), FALSE, ExcludeMotion)) -> df
  
head(df)
```

Brief Variable Descriptions:

`CCID` = string, CamCan Subject ID  
`anat_T1w`:`fmap_smt_NA` = logical, whether or not a specific MRI image exists  
`DetPosPic`:`TotalDetRecalls` = double, number of detailed recalls during the Emotional Memory Task  
`Age`:`MT_TR` = misc, demographic data provided by CamCan  
`Ntrials`:`RA` = misc, Cattell Fluid Intelligence Test data  
`additional_attention_orientation`:`additional_acer` = double, ACE-R test scores  

## How many subjects do we have?

```{r}
# each row = subject
nrow(df)
```
## How many subjects are usuable?

```{r}
# Create a new column that indicates where each participants has at least one missing scan
df %>% 
  rowwise() %>% 
  mutate(AnyMissingMRI = !all(c_across(cols = anat_T1w:fmap_smt_NA))) %>% 
  ungroup() -> df

df %>%
  ungroup() %>%
  mutate(AgeExclusion = Age > age_thresh) -> df

# Determine who has missing Emotional Memory data
df %>%
  rowwise() %>%
  mutate(AnyMissingEmoMem = is.na(TotalDetRecalls)) -> df

# Determine who has missing Wechler Memory Data
df %>%
  mutate(AnyMissingWechler = any(is.na(homeint_v219), is.na(homeint_v515), is.na(homeint_storyrecall_i), is.na(homeint_storyrecall_d))) -> df

# Determine who has missing Cattell data
df %>%
  mutate(AnyMissingCattell = is.na(TotalScore)) -> df

# Determine who has missing ACR-R data
df %>%
  mutate(AnyMissingAdd = is.na(additional_memory)) -> df

# Determine who meets preliminary inclusion criterion -- no missing data
df %>%
  mutate(MeetsInclusionCriterion = !any(AnyMissingMRI, AnyMissingEmoMem, AgeExclusion, AnyMissingAdd, ExcludeMotion)) -> df
```

```{r}
# Hand Code a Sankey Diagram

# Hand write the nodes data frame
nodes <- data.frame(node = 0:11, 
                    name = c('All Subjects', 
                             'Has All MRI Data', 'Missing At Least One Image',
                             'Low Motion', 'High Motion',
                             str_glue('Under Age {age_thresh}'), str_glue('Over Age {age_thresh}'),                             
                             'Has Weschler', 'Missing Weschler',
                             'Has Emotional Memory', 'Missing Emotional Memory', 
                             'Meets Inclusion Criteria'),
                    node_group = c('1', '1', '2', '1', '2', '1', '2', '1', '2', '1', '2', '1'))

# Links

## Missing MRI data

df %>% 
  ungroup() %>% 
  count(AnyMissingMRI) %>%
  pull() -> val
  
links <- data.frame(source = c(0, 0), target = c(1,2), value = val)

## Gross Motion

df %>%
  filter(!AnyMissingMRI) %>%
  count(ExcludeMotion) %>%
  pull(n) -> val

links %>%
  add_row(source = c(1,1), target = c(3,4), value = val) -> links

## Age Restriction

df %>%
  filter(!AnyMissingMRI) %>%
  filter(!ExcludeMotion) %>%
  count(AgeExclusion) %>%
  pull(n) -> val

links %>%
  add_row(source = c(3,3), target = c(5,6), value = val) -> links

## Missing Wechler

df %>%
  filter(!AnyMissingMRI) %>%
  filter(!ExcludeMotion) %>%
  filter(!AgeExclusion) %>%
  mutate(AnyMissingWechler = factor(AnyMissingWechler, levels = c(FALSE, TRUE), labels = c(FALSE, TRUE))) %>% 
  count(AnyMissingWechler) %>%
  complete(AnyMissingWechler, fill = list(n = 0)) %>%
  pull(n) -> val

links %>%
  add_row(source = c(5,5), target = c(7,8), value = val) -> links

## Missing Missing Emo Mem

df %>%
  filter(!AnyMissingMRI) %>%
  filter(!ExcludeMotion) %>%
  filter(!AgeExclusion) %>%
  filter(!AnyMissingWechler) %>%
  count(AnyMissingEmoMem) %>%
  pull(n) -> val

links %>%
  add_row(source = c(7,7), target = c(9,10), value = val) -> links

## 

links %>%
  add_row(source = 9, target = 11, value = val[1]) -> links

networkD3::sankeyNetwork(Links = links, Nodes = nodes, 
                         Source = 'source', 
                         Target = 'target', 
                         Value = 'value', 
                         NodeID = 'name', 
                         units = 'subjects', 
                         NodeGroup = 'node_group', sinksRight = FALSE, fontSize = 12)
```

Of the `r nrow(df)` subjects, `r df %>% pull(MeetsInclusionCriterion) %>% sum()` meet the preliminary inclusion of having no missing data on our variables of interest. See the Sankey Diagram above to see why participants were excluded.  

## How correlated are the behavioral variables?

```{r paged.print=TRUE}
df %>%
  filter(MeetsInclusionCriterion) %>%
  mutate(Sex = factor(Sex)) %>%
  mutate(Sex = as.numeric(Sex)) %>%
  select(Age, Sex, TotalDetRecalls, TotalScore, additional_memory, homeint_storyrecall_d) %>%
  corrr::correlate(quiet = TRUE)
```

## What is the demographics breakdown of the subjects who meet are inclusion criteria?

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  mutate(AgeBins = cut(Age, breaks = c(18, 28, 38, 48, 58, 68, 78, 89))) %>%
  select(AgeBins, Sex) %>%
  table()
```

## How much variability is there in the subjects who meet our inclusion criteria?

### Emotional Memory Recalls

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  ggplot(aes(x = TotalDetRecalls)) +
  geom_histogram(bins = 30) +
  labs(title = 'Emotional Memory: Number of Detailed Recalls')
```

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  pull(TotalDetRecalls) %>%
  psych::describe() %>%
  tibble() %>%
  select(-vars)
```

### Emotional Memory Recalls

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  ggplot(aes(x = homeint_storyrecall_d)) +
  geom_histogram(bins = 30) +
  labs(title = 'Logical Portion of Wechler Memory Scale: Number of Items Recalled', subtitle = 'After 20 Min Delay')
```

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  pull(homeint_storyrecall_d) %>%
  psych::describe() %>%
  tibble() %>%
  select(-vars)
```

## Is this variability related to Age?

### Emotional Memory

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  ggplot(aes(Age, TotalDetRecalls)) +
  geom_point() +
  geom_smooth(method = lm, formula = y ~ x) +
  labs(title = 'Is Memory Ability Related to Age?', subtitle = 'Yes')
```

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  lm(TotalDetRecalls~Age, data = .) %>%
  summary()
```

### Weschler

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  ggplot(aes(Age, homeint_storyrecall_d)) +
  geom_point() +
  geom_smooth(method = lm, formula = y ~ x) +
  labs(title = 'Is Memory Ability Related to Age?', subtitle = 'Yes')
```

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  lm(homeint_storyrecall_d~Age, data = .) %>%
  summary()
```

## Is this varaibility related to sex?

### Emotional Memory

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  ggplot(aes(Sex, TotalDetRecalls)) +
  geom_boxplot() +
  labs(title = 'Is memory related to sex?', subtitle = 'Yes')
```

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  t.test(TotalDetRecalls~Sex, data = .)
```

### Weschler

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  ggplot(aes(Sex, homeint_storyrecall_d)) +
  geom_boxplot() +
  labs(title = 'Is memory related to sex?', subtitle = 'Yes')
```

```{r}
df %>%
  filter(MeetsInclusionCriterion) %>%
  t.test(homeint_storyrecall_d~Sex, data = .)
```

## Motion

The functional scans for CamCan look as follows:

Movie Task 
`CamCan/sub-CC#####/func/sub-CC#####_task-movie_echo-1_bold.nii`
`CamCan/sub-CC#####/func/sub-CC#####_task-movie_echo-2_bold.nii`
`CamCan/sub-CC#####/func/sub-CC#####_task-movie_echo-3_bold.nii`
`CamCan/sub-CC#####/func/sub-CC#####_task-movie_echo-4_bold.nii`
`CamCan/sub-CC#####/func/sub-CC#####_task-movie_echo-5_bold.nii`

Rest Task
`CamCan/sub-CC#####/func/sub-CC#####_task-rest_bold.nii`


SMT Task
`CamCan/sub-CC#####/func/sub-CC#####_task-SMT_bold.nii`

## What does gross motion look like for the different scans?

```{r}
motion %>% 
  filter(task == 'movie') %>%
  group_by(CCID) %>%
  summarise(BadMotion = sum(fd_mean > fd_mean_thresh), .groups = 'drop') %>%
  mutate(BadMotion = BadMotion > num_runs_thresh) %>%
  add_column(task = 'movie') -> movie

motion %>%
  filter(task != 'movie') %>%
  mutate(BadMotion = fd_mean > fd_mean_thresh) %>%
  select(CCID, task, BadMotion) %>%
  bind_rows(., movie) %>%
  ggplot(aes(x = task, fill = BadMotion)) +
  geom_bar() +
  labs(y = 'Numbers of Subjects', x = 'Task')
```

## What does gross motion look like for the multi-echo movie data?

```{r}
motion %>% 
  filter(task == 'movie') %>%
  group_by(CCID) %>%
  summarise(BadMotion = sum(fd_mean > fd_mean_thresh), .groups = 'drop') %>%
  mutate(MotionFilter = BadMotion == 0,
         MotionFilter = factor(MotionFilter, levels = c(T,F), labels = c('Included', 'Excluded'))) %>%
  ggplot(aes(x = BadMotion, fill = MotionFilter)) +
  geom_histogram(bins = 30) +
  labs(title = 'Number of Motion Corrupted Scans',
       subtitle = "In CamCan's Multiecho Movie Watching Data",
       y = 'Number of Subjects',
       x = 'Number of Echos with fd_mean > 0.2')
```

